Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-11-18 doc/Paper/main.tex
Added footnote explaining s(z) notation.

    In the presence of magnification, the equations presented in Section \ref{ssec:methods.theory} acquire additional terms. The projected galaxy overdensity becomes:
    \begin{equation}
      \delta^i_g(\nv)=\int \mathrm{d}z\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
    \end{equation}
    where $\Delta_m$ is the 3D matter overdensity (we have omitted the dependence on $t$ and $\chi\nv$ for brevity) and $W_\mu$ is the magnification kernel
    \begin{equation}
      W_\mu(z)=\frac{3H_0^2\Omega_{m}(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
    \end{equation}
    Here, $H_0\equiv H(z=0)$, $\Omega_{m}$ is the fractional matter density today, and $s$ is the logarithmic slope of the cumulative apparent magnitude distribution $N(<m, z)$:
    \begin{equation}
      \left. s(z) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m}\right \rvert_{m=m_{\mathrm{lim}}},
      \label{eq:s-func}
    \end{equation}
    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered. In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies. Overdensities along the line of sight cause the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increasing the observed number density). The two effects cancel at leading order when $s=\sfrac{2}{5}$.

>>>>

    In the presence of magnification, the equations presented in Section \ref{ssec:methods.theory} acquire additional terms. The projected galaxy overdensity becomes:
    \begin{equation}
      \delta^i_g(\nv)=\int \mathrm{d}z\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
    \end{equation}
    where $\Delta_m$ is the 3D matter overdensity (we have omitted the dependence on $t$ and $\chi\nv$ for brevity) and $W_\mu$ is the magnification kernel
    \begin{equation}
      W_\mu(z)=\frac{3H_0^2\Omega_{m}(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
    \end{equation}
    Here, $H_0\equiv H(z=0)$, $\Omega_{m}$ is the fractional matter density today, and $s$ is the logarithmic slope of the cumulative apparent magnitude distribution $N(<m, z)$:
    \begin{equation}
      \left. s(z) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m}\right \rvert_{m=m_{\mathrm{lim}}},
      \label{eq:s-func}
    \end{equation}
    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered\footnote{In the following, we omit the dependence of $s(z)$ on $m_{\mathrm{lim}}$ for brevity.}. In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies. Overdensities along the line of sight cause the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increasing the observed number density). The two effects cancel at leading order when $s=\sfrac{2}{5}$.
